\section{Apendix}

We will not pay our Members of the Board. The Board has the authority to form committees to address particular issues. A committee can be formed at the request of any Member of the Board or the CEO and the person requesting the formation of the committee might make non-binding recommendations on its composition. We will likely have permanent committees, for example to review grant applications, but are stated as ad hoc in the by laws to provide maximum flexibility.

The Institute will maintain work relations with individuals that can help to advance its mission. Such positions include that of Technical Expert, Industry Leader and Role Model. There is no affiliation requisite for these positions. They help us with our incubator, going to local high schools and universities or in any other way finding promising, underserved students who either have and idea for the incubator or could get behind an idea. The project in the incubator should be something that would benefit society in general or a sector of society. We will not pay people helping us in this capacity but we can pay for outreach or operating costs.

The Institute will have permanent scientists and other thought leaders officially and permanently affiliated to the Institute. Grant-seeking will occur through the Institue and the scientist will stipulate his or her salary in the grant proposal. Each application will be reviewed by the Board of Directors or a committee created by the Board of Directors.

The Institute will have officers with some administrative duties. Officer positions might include: treasurer, Chief Technology Officer, Chief Science Officer, Chief Diversity Officer, etc. We don't have money right now, but we expect these positions to be full-time and paid in the future. The positions are created as needed by the CEO. 

\subsection{Definitions}

\textbf{Transdisciplinary.} Collaboration in which exchanging information, altering discipline-specific approaches, sharing resources and integrating disciplines achieves a common scientific goal (Rosenfield 1992).

\textbf{Multidisciplinary.} Researchers from a variety of disciplines work together at some point during a project, but have separate questions, separate conclusions, and disseminate in different journals.

\textbf{Interdisciplinary.} Researchers interact with the goal of transferring knowledge from one discipline to another. Allows researchers to inform each other’s work and compare individual findings.
    