\section{Bylaws of The Datum Institute}

June 15, 2015

\subsection{Board of Directors}

The activities and affairs of The Datum Institute (referred to in this and the following sections as the "Institute") shall be conducted by and all corporate powers shall be exercised by or under the direction of the Board of Directors (sometimes referred to as the "Board"). The authorized number of members of the Board shall be at least three and no more than ten. 

\begin{enumerate}[(a)]
\item Board Powers

In addition to the general powers conferred by these Bylaws, the specific powers and duties of the Board of Directors shall include:

\begin{enumerate}
\item Election, appointment or removal of members of the Board, Chief Executive Officer of the Institute and committee members; 
\item Determination of policy;
\item Review of reports from the Chief Executive Officer for assurance that such policy is being executed;
\item Power to act directly on any matter in event of emergency;
\item Assistance in raising funds to support the Institute;
\end{enumerate}

The affirmative vote of a majority of the members of the Board in office shall be required to remove a member of the Board from office.

\item Director

\begin{enumerate}
\item Qualifications

The Directors shall have the qualifications provided in the Articles of Incorporation and these Bylaws. 

\item Terms of Office

Directors shall serve for three-year terms and may succeed themselves in office.  A vacancy in any Director position may be filled at any time for the remainder of the term by the remaining members of the Board or be left vacant if at least three Directors remain.

\end{enumerate}

\item Chairman of the Board of Directors and Other Board Positions Designated

The Board shall elect one of its members to be Chairman of the Board of Directors and may elect one or more Vice-Chairs.

\end{enumerate}

\subsection{Officers}

\begin{enumerate}[(a)]
\item Officers

The Corporate Officers of the Institute shall be a Chair of the Board of Directors, such number of Vice Chairs of the Board as the Board may determine, a President, a Provost, a Vice President for Business and Finance, a Vice President for Development and Institute Relations, a Vice President for Student Affairs, a Vice President and Director of the Jet Propulsion Laboratory, a General Counsel, a Controller, a Treasurer, a Chief Investment Officer, a Secretary, and, at the discretion of the President, there may be a Vice President for Strategy Implementation.  There may be other Vice Presidents, Assistant Controllers, Assistant Treasurers, Assistant Secretaries, and such other Officers deemed necessary for proper management of the affairs of the Institute.  All Officers shall be elected by the Board.  The Chair and each Vice Chair shall be members of the Board.  The Chair and each Vice Chair shall be elected each year by the Board at its Annual Meeting for a term of office which shall expire on, but shall include, the date of its Annual Meeting next succeeding such election.  Unless the Board otherwise determines, the other Officers, except the President, need not be members of the Board; and all shall hold their offices at the pleasure of the Board.
\end{enumerate}

