\textit{}\section{Bylaws of The Datum Institute}

June 15, 2015

\subsection{Board of Directors}

The activities and affairs of The Datum Institute (referred to in this and the following sections as the "Institute") shall be conducted by and all corporate powers shall be exercised by or under the direction of the Board of Directors (sometimes referred to as the "Board"). The authorized number of members of the Board shall be at least three and no more than ten. The board receives no compensation other than reasonable expenses. 

\begin{enumerate}[(a)]
\item Board Powers

In addition to the general powers conferred by these Bylaws, the specific powers and duties of the Board of Directors shall include:

\begin{enumerate}
\item Election, appointment or removal of members of the Board, officers and committee members; 
\item Determination of policy;
\item Review of reports from the Chief Executive Officer for assurance that such policy is being executed;
\item Power to act directly on any matter in event of emergency;
\item Assistance in raising funds to support the Institute;
\end{enumerate}

The affirmative vote of a majority of the members of the Board in office shall be required to remove a member of the Board from office.

\item Director

\begin{enumerate}
\item Qualifications

The Directors shall have the qualifications provided in the Articles of Incorporation and these Bylaws. 

\item Terms of Office

Directors shall serve terms that end the day after their third annual meeting and may succeed themselves in office.  A vacancy in any director position may be filled at any time for the remainder of the term by the remaining members of the Board or be left vacant if at least the minimum number of directors established by these bylaws remain.

\end{enumerate}

\item Chairman of the Board of Directors

The Board shall elect one of its members to be Chairman of the Board of Directors. The Chairman shall hold office at the pleasure of the Board of Directors and until a successor shall have been duly elected and qualified, unless sooner removed, and may be removed at any time by the Board of Directors. The Chairman of the Board of Directors may succeed him or herself in office.

\end{enumerate}

\subsection{Officers}

\begin{enumerate}[(a)]
\item Officers

The Corporate Officers of the Institute shall be a Chief Executive Officer, a Chief of Staff, and such other officers as the Board of Directors may deem expedient, and such officers shall be elected in such manner and hold their offices for such terms as the Board of Directors may prescribe.

\item Officers' Powers and Duties

Each Officer shall have such powers and duties vested in that office by the provisions of these Bylaws and such additional powers and duties as the Board may confer in that office.

\begin{enumerate}
\item The Chairman of the Board shall preside at the Board meetings; act as the representative of the Board in dealing with the administration of the Institute and with its publics; foster communication with the administration; maintain especially close liaison with the Chief Executive Officer, being available for advice and support at all times, particularly in external affairs; act as the representative of the Board in event of an emergency.

\item The Chief Executive Officer shall preside over and administer the affairs of the Institute under authority of the Board; serve at the pleasure of the Board; execute decisions and policies as designated by the Board; keep the Board informed of administrative, research, outreach and other pertinent affairs; submit recommendations to the Board on matters of policy; establish and maintain relationships with the public; have the freedom to propose the creation of officer positions to the Board; have the freedom to propose persons for election as officers, with the exception of Chair of the Board and the Chief Executive Officer; creates research positions.

\item The Chief of Staff should be responsible to the Chief Executive Officer; have the power to act for the Chief Executive Officer when the Chief Executive Officer is absent or incapacitated; recommend policies and administer procedures concerning Institute programs, including research and outreach; recommend research position appointments to the Chief Executive Officer.
\end{enumerate}



\end{enumerate}

\subsection{Meetings of the Board}
\begin{enumerate}[(a)]
\item Regular Meetings

Regular meetings of the Board of Directors shall be held as determined by action of the Board.

\item Annual Meetings

An annual meeting of the members shall take place in the month of October, the specific date, time and location of which will be designated by the chair. At the annual meeting the members shall elect directors, officers and committees of the Board, receive reports on the activities of the corporation, and determine the direction of the association for the coming year.

\item Board Elections

New directors and current directors shall be elected or re-elected by the members at the annual meeting. Directors will be elected by a simple majority of members present at the annual meeting. The Chairman of the Board shall be responsible for nominating prospective board members and any member can nominate a candidate. 

\item Quorum and Participation

The directors in attendance at a meeting shall constitute a quorum if the number is at least two. A director may participate in a Board meeting by conference telephone or similar communications equipment and may vote, as long as all directors participating in the meeting can clearly hear and communicate with each other.

\end{enumerate}

\subsection{Committees}
\begin{enumerate}[(a)]
\item Special Committees

The board may create whatever committees it considers necessary to assist it in fulfilling its governance accountability.

\end{enumerate}
    
\subsection{Bylaws changes}

These Bylaws may be amended or repealed, or new Bylaws may be adopted, by the Board at any meeting of the Board.

    
    
    
    
    
    
    
    